Measuring Subgroup Preferences in Conjoint Experiments\footnote{We thank Benjamin Lauderdale, Jamie Druckman, Yusaku Horiuchi, the editor, and anonymous reviewers for feedback on this manuscript.}

### 2019-04-11 manuscript.tex
add in Bechtel and Scheve example; update figures; edit

\usepackage{alltt}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
%\usepackage{times}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage[normalem]{ulem}
\usepackage{sectsty}
\subsectionfont{\normalfont\large\underline}
\usepackage{floatrow}
\floatsetup[figure]{capposition=top}
\floatsetup[table]{capposition=top}

\title{Measuring Subgroup Preferences in Conjoint Experiments}
\author{Thomas J. Leeper, Sara B. Hobolt, and James Tilley}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

Conjoint analysis serves two purposes. One is to assess causal effects. Another is preference description.\footnote{Here we use ``preference'' as \citet{HainmuellerHopkinsYamamoto2014} do: that is, as a statement of \textit{favorability} or \textit{support} for a profile, not the more narrow economic definition of a strict rank ordering of objects by favorability.} In causal inference, conjoints provide a design and analytic approach that allows researchers to understand the causal effect of a given feature on overall support for a multidimensional object, averaging across other features of the object included in the design. Such inferences can be thought of as statements of the form: ``shifting an immigrant's country of origin from India to Poland increases favorability by X percentage points.'' In descriptive inference, conjoints provide information about both (a) the \textit{absolute} favorability of respondents toward objects with particular features or combinations of features, and (b) the \textit{relative} favorability of respondents toward an object with alternative combinations of features. Such inferences can be thought of as statements of the form ``Polish immigrants are preferred by X\% of respondents'' or ``Polish immigrants are more supported than Mexican immigrants, by X percentage points.'' Thus both causal and descriptive interpretations of conjoints are based upon the distribution of preferences across profile features and differences in preferences across alternative feature combinations.

Importantly, a fully randomized conjoint design without constraints between profile features is simply a full-factorial experiment (with some cells possibly, albeit randomly, left unobserved). All quantities of interest relevant to the analysis of conjoint designs derive from combinations of cell means, marginal means, and the grand mean, as is common in the traditional analysis of factorial experiments. In a forced choice design, the \textit{grand mean} is by definition 0.5 (i.e., 50\% of all profiles shown are chosen and 50\% are not chosen). \textit{Cell means} are the mean outcome for each particular combination of feature levels. In the full-factorial design discussed by \citet{HainmuellerHopkinsYamamoto2014} and now widely used in political science, many or perhaps most cell means are unobserved. For example, in their candidate choice experiment, there are $2*6*6*6*2*6*6*6 = 186,624$ cell means but only 3,466 observations so about 98\% of cell means are unobserved. While this would be problematic for attempting to infer pairwise comparisons between cells, conjoint analysts mostly focus on the marginal effects of each feature rather than more complex interactions. Appendix \ref{app:quantities} provides detailed notation and elaborations of these definitions of quantities of interest.

Average marginal component effects (AMCEs) depend only upon \textit{marginal means}: that is the column and row mean outcomes for each feature level averaging across all other features. A marginal mean describes the level of favorability toward profiles that have a particular feature level, marginalizing across all other features. For example, in the common forced-choice design with two alternatives, marginal means have a direct interpretation as probabilities: a marginal mean of 0 indicates respondents select profiles with that feature level with probability $Pr(Y=1|X=x) = 0$ while a marginal mean of 1 indicates respondents select profiles with that feature level with probability $(Pr(Y=1|X=x)=1$.\footnote{It is not possible for the marginal mean to equal zero or one if pairs of profiles shown together are allowed to have the same level of a given feature (for example, both immigrants are from Germany). Instead, the marginal mean can range from the probability of co-occurrence to 1 minus that probability. If there are five levels of a feature, each shown with equal probability, then the probability of co-occurrence is $\frac{1}{5}*\frac{1}{5} = 0.04$ such that the marginal mean can take values in the range $(0.04,0.96)$. If the design is constrained so that features cannot be the same for both immigrants, then the marginal means fully range from zero to one. This constraint on the range of the marginal means also constrains the range of AMCEs. Notably, many conjoints provide features with only two levels, such as the male-versus-female candidate feature examined by \citet{TeeleKallaRosenbluth2018}. In such cases, the probability of co-occurrence is $\frac{1}{2}*\frac{1}{2} = 0.25$ bounding the AMCE for female (as opposed to male) candidates to the range $(-0.5, 0.5)$ if both candidates can have the same sex. Caution is therefore needed in comparing the relative size of features with few levels to features with many levels given that effects have different bounds.} With rating scale outcomes, marginal means can vary arbitrarily along the outcome scale used.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
\includegraphics[width=\maxwidth]{figure/hainmueller_candidate_replication-1} 
\includegraphics[width=\maxwidth]{figure/hainmueller_candidate_replication-2} \caption[Replication of Hainmueller et al]{Replication of Hainmueller et al. (2014) Candidate Experiment using AMCEs and MMs}\label{fig:hainmueller_candidate_replication}
\end{figure}

@@

Because levels of features are randomly assigned, pairwise differences between two marginal means for a given feature (e.g., between candidates who are male versus female) have a direct causal interpretation. For fully randomized designs, the AMCE proposed by \citet{HainmuellerHopkinsYamamoto2014} is equivalent to the average marginal effect of each feature level for a model where each feature is converted into a matrix of indicator variables with one level left out as a reference category. This is no different from any other regression context wherein one level of any categorical variable must be omitted from the design matrix in order to avoid perfect multicollinearity.\footnote{In designs that entail constraints between profile features, the average marginal effect is a weighted average of effects across each combination of the constrained features where the weights on the effects are arbitrary but typically uniform. We ignore this distinction in the remainder of this article, as all of our results apply equally to fully randomized and to constrained designs.} This close relationship between AMCEs and marginal means is visible in Figure \ref{fig:hainmueller_candidate_replication} which presents a replication of the AMCE-based analysis of the Hainmueller et al. candidate experiment (upper panel) and an analogous examination of the results using marginal means (lower panel). Here and throughout we use visual presentation of results, but full numerical estimates including appropriate standard errors are presented in the Appendix. Note, in particular, how marginal means convey information about the preferences of respondents for all feature levels while AMCEs definitionally restrict the AMCE for the reference category to zero (or undefined). For example, the AMCE for a candidate serving in the military is 0.09 (or a 9-percentage point) increase in favorability, reflecting marginal means for serving and non-serving candidates of 0.46 and 0.54, respectively.

The AMCE is often described as an estimate of the relative favorability of profiles with counterfactual levels of a feature; for example, ``male candidates are preferred to female candidates'' \citep[6]{TeeleKallaRosenbluth2018}. \citet{HainmuellerHopkinsYamamoto2014} similarly describe some of the results of conjoint on preferences toward Congressional candidates:

@@

\noindent These examples make clear that despite the \textit{causal} inference potentially provided by the AMCE, the quantity of interest is frequently used to provide a characterization of a preferences that has a distinctly descriptive flavor. Indeed, this style of description is widespread in conjoint analyses. \citet{BallardRosaMartinScheve2016} interpretation their tax preference conjoint:

\begin{quote}
we find strong support for progressive preferences over federal income taxes among the American public [\dots] respondents are less likely to support a given tax plan as the tax rate on the poorest three groups increases but more likely to support an income tax policy when the tax rate on the richest two groups increases, at least to a point.
\end{quote}

\noindent This use of conjoints to provide descriptive inferences about patterns of preferences is important because AMCEs are defined as \textit{relative} quantities, requiring that patterns of preferences are expressed against a baseline, reference category for each conjoint feature. A positive (negative) AMCE is read as higher (lower) favorability but it is only higher (lower) relative to whatever category serves as the baseline. For example, in the \citeauthor{HainmuellerHopkinsYamamoto2014} candidate example, choosing a non-religious candidate as a baseline means the AMCEs in the candidate experiment are all expressed relative to this non-religious baseline; the difference (if any) between other pairs of marginal means (e.g., evaluations of Mormon and Evangelical candidates) is not obvious. Relatedly, the negative direction (and the size) of the AMCEs for Mormon and Evangelical candidates would be different if the least-liked category (Mormon candidates) were the reference group. In that case, the AMCE for Evangelicals would be small and positive and the AMCEs for all other categories (including the presented reference category, ``none'') would be large and positive.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
\includegraphics[width=\maxwidth]{figure/reference_category-1} \caption[Reference Category Diagnostic for the 'Education' Feature from Hainmueller et al.'s (2014) Immigration Experiment]{Reference Category Diagnostic for the 'Education' Feature from Hainmueller et al.'s (2014) Immigration Experiment}\label{fig:reference_category}
\end{figure}

@@

Being a familiar analytic problem in any regression context, this choice of reference category for estimating AMCEs can seem trivial but is quite consequential. For example, in \citeauthor{HainmuellerHopkinsYamamoto2014}'s candidate experiment, the least liked education level (``no formal education'') is chosen as a reference category, but the authors could have presented the results using any of the categories as the baseline. Figure \ref{fig:reference_category} shows how the estimated AMCEs for each level of education would have differed depending on that choice. Selecting a reference category that receives middling support (i.e., more favorability than some other feature levels but less favorability than others), makes some AMCEs positive and others negative but all AMCEs can be made positive (or negative) simply by choosing a different baseline.\footnote{As another example, in \citeauthor{BallardRosaMartinScheve2016}'s tax preference experiment, the lowest level of taxation is chosen as the reference category for each feature for reasons of substantive interpretation, yet despite the substantive intuitiveness of this, favorability toward the lowest level of taxation is not necessarily higher or lower than preferences for alternative tax rates.} The results would be numerically equivalent --- the alternative linear models used to the estimate the AMCEs have a mathematical equivalence --- but the choice has sizeable consequences for the interpretation of conjoint analyses, as we discuss below.\footnote{In \textit{constrained} conjoint designs, the choice of reference category is even more important. Consider, for example, the design of \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment, which constrains the ``Country of Origin`` feature so that levels `India,' `Germany,' `France,' `Mexico,' `Philippines,' and `Poland' cannot co-occur with the `Escape Persecution' level of the ``Reason for Application'' feature. Consequently, the AMCE for the ``Escape Persecution'' level (relative to the  ``Reunite with family'' reference category) is only defined for the subset of the design involving countries `China,' `Sudan,' `Somalia,' and `Iraq.' The AMCEs for those four countries (relative to India as a baseline) marginalize across all reasons for application, but the AMCEs for the first six countries marginalize only across the latter two reasons. Thus the interpretation of AMCEs --- and the basic ability to estimate them in constrained designs --- depends entirely upon the selection of a reference category where all feature levels can co-occur. In a design where \textit{all} features are constrained, then AMCEs are undefined for the design as a whole and only estimable for subsets of the design that are \textit{conditionally} unconstrained.}

@@

Given the need to choose a reference category for every feature in order to estimate AMCEs, an important question is: how do researchers decide which of tens of thousands of possible experimental cells should be selected as the reference category? Examining recently published conjoint analyses, it appears that the choice of reference category is either arbitrary or based upon substantive intuition about the meaning of feature levels. For example, \citet{HainmuellerHopkinsYamamoto2014} choose female immigrants as a baseline in their immigration experiment, thus providing an estimate of the AMCE of being male, while \citet{TeeleKallaRosenbluth2018} choose male candidates as a baseline in their conjoint, thus providing an estimate of the AMCE of being female. The choice is seemingly innocuous. Sometimes choices of reference category appear to be driven by substantive knowledge: on language skills of immigrants, \citet{HainmuellerHopkinsYamamoto2014} choose fluency as a baseline; on the prior trips to the US feature, ``never'' is chosen as the baseline. These seem sensible on face value --- it might seem less useful to define all effects relative to ``having visited many times as a tourist'' as the AMCEs then lose an immediately intuitive interpretation.

% Difference in conditional AMCEs
\begin{table}
\caption{Uses of Subgroup Analysis Published in Political Science Journals}\label{tab:papers}
\begin{center}
\footnotesize
\begin{tabular}{p{2in} p{2in} p{2in}}\toprule
\textbf{Paper} & \textbf{Topic} & \textbf{Subgroup Comparisons} \\ \midrule
\citet{BechtelScheve2013} & Climate agreement preferences & Environmentalism and International Reciprocity Attitudes \\ \midrule
\citet{FranchinoZucchini2014} & Candidate preferences & Political Interest, Left-right self-placement\\ \midrule
\citet{HainmuellerHopkinsYamamoto2014} & Immigration preferences & Ethnocentrism \\ \midrule
\citet{HansenOlsenBech2014} & Policy preferences & Partisanship \\ \midrule
\citet{Carlson2015} & Candidate preferences & Co-ethnicity \\ \midrule
\citet{BansakHainmuellerHangartner2016} & Immigration preferences & Left-right self-placement, age, education, income\\ \midrule
\citet{BallardRosaMartinScheve2016} & Tax preferences & Various\\ \midrule
\citet{Campbelletal2016} & Candidate preferences & Partisanship \\ \midrule
\citet{CarnesLupu2016} & Candidate preferences & Partisanship \\ \midrule
\citet{Mummolo2016} & News selection & Various\\ \midrule
\citet{VivyanWagner2016} & Candidate preferences & Political attitudes \\ \midrule
\citet{MummoloNall2017} & Mobility preferences & Partisanship \\ \midrule
\citet{BechtelGenoveseScheve2017} & Climate agreement preferences & Employment sector emissions \\ \midrule
\citet{BechtelHainmuellerMargalit2017} & International bailout preferences & Various\\ \midrule
\citet{GallegoMarx2017} & Labor market policy & Left-right self-placement \\ \midrule
\citet{KirklandCoppock2017} & Candidate preferences & Partisanship \\ \midrule
\citet{Sen2017} & Judicial candidate preferences & Partisanship \\ \midrule
\citet{Sobolewskaetal2017} & Immigrant integration & Various \\ \midrule
\citet{EggersVivyanWagner2018} & Candidate preferences & Sex \\ \midrule
\citet{Hankinson2018} & Housing policy preferences & Various \\ \midrule
\citet{OliverosSchuster2018} & Bureaucrat candidate preferences & Various \\ \midrule
\citet{TeeleKallaRosenbluth2018} & Candidate preferences & Sex, Partisanship \\ \midrule
\citet{Careyetal2018} & Hiring preferences & Various \\ \midrule
\bottomrule
\end{tabular}
\end{center}
All articles in this table use subgroup conditional AMCEs to make inferences about differences in preferences between subgroups.
\end{table}

Yet the choice is consequential. A possibly surprising consequence of the seemingly arbitrary selection of a reference category --- and the resulting arbitrariness of both the size and direction of AMCEs --- is that it can provide highly distorted descriptive interpretation of preferences among subgroups of respondents. This occurs when researchers examine \textit{conditional} AMCEs, wherein AMCEs are calculated separately for subgroups of respondents and those conditional estimates are directly compared \citep[13]{HainmuellerHopkinsYamamoto2014}. Table \ref{tab:papers} reports a list of recently published articles in political science that engage in this form of subgroup analysis.\footnote{\citet{RatkovicTingley2017} considered efficient methods for performing subgroup analyses in conjoint designs. Our focus here is on the narrower problem of interpreting subgroup analyses as traditionally performed using subsetting or interaction terms in a regression framework.} Given the commonly descriptive interpretations of conjoint experimental results, such subgroup analyses seem perfectly intuitive and the set of subgroups listed in the last column of Table \ref{tab:papers} contains some unsurprising covariates, such as partisanship, that are of obvious theoretical interest in almost any study of individual preferences. Analytically, these conditional AMCEs can be obtained either from regression estimates on respondent subgroups or through interactions between conjoint features and respondent characteristics, the details of which are unimportant for our purposes.

Conditional AMCEs are not per se a problematic quantity of inference. Like subgroup analysis of any experiment, they convey the causal effect of an experimental factor on overall favorability among the subgroup of interest. Consider, for example, a two-condition party cue experiment where Democrats and Republicans are exposed to an endorsement cue from the Democratic party or no cue and opinions toward the policy serve as the outcome. It is sensible to imagine that effects of the cue might differ for the two groups and therefore to compare the size of cue effect among the two groups. Perhaps Democrats are more responsive to the Democratic party cue than are Republicans, making the causal effect larger for Democrats than Republicans. Discussions of conditional AMCEs in conjoint analyses often explicitly or implicitly engage in this kind of discussion comparing the size and direction of subgroup causal effects. If interpreted as a difference in the size of the causal effect for two groups, such comparisons are perfectly consistent with more traditional experimental analysis and a perfectly acceptable interpretation of the conjoint results.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
\includegraphics[width=\maxwidth]{figure/tkr_replication-1} 
\includegraphics[width=\maxwidth]{figure/tkr_replication-2} \caption[Replication of Teele et al]{Replication of Teele et al. (2018) Candidate Experiment using AMCEs and MMs}\label{fig:tkr_replication}
\end{figure}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
\includegraphics[width=\maxwidth]{figure/hainmueller_mm_by_ethnocentrism-1} \caption[Conditional Marginal Means, by Ethnocentrism, for Hainmueller et al.'s (2014) Immigration Experiment]{Conditional Marginal Means, by Ethnocentrism, for Hainmueller et al.'s (2014) Immigration Experiment}\label{fig:hainmueller_mm_by_ethnocentrism}
\end{figure}

@@

\item Exercise caution when explicitly or implicitly interpreting differences-in-AMCEs across subgroups. While that quantity conveys the difference in effects of a change in a given feature, heterogeneous effects do not necessarily mean different underlying preferences. Differences-in-AMCEs are almost always a biased estimate (of unknown sign and direction) of the difference in underlying preferences. If differences in AMCEs are reported, the choice of reference categories should be discussed explicitly and diagnostics should be provided to justify it.

@@

>>>>

\usepackage{alltt}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mathpazo}
%\usepackage{times}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage[normalem]{ulem}
\usepackage{sectsty}
\subsectionfont{\normalfont\large\underline}
\usepackage{floatrow}
\floatsetup[figure]{capposition=top}
\floatsetup[table]{capposition=top}

\title{Measuring Subgroup Preferences in Conjoint Experiments\footnote{We thank Benjamin Lauderdale, Jamie Druckman, Yusaku Horiuchi, the editor, and anonymous reviewers for feedback on this manuscript.}}
\author{Thomas J. Leeper, Sara B. Hobolt, and James Tilley}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

Conjoint analysis serves two purposes. One is to assess causal effects. Another is preference description.\footnote{Here we use ``preference'' as \citet{HainmuellerHopkinsYamamoto2014} do: that is, as a statement of \textit{favorability} or \textit{support} for a profile, not the more narrow economic definition of a strict rank ordering of objects by favorability.} In causal inference, fully randomized conjoints provide a design and analytic approach that allows researchers to understand the causal effect of a given feature on overall support for a multidimensional object, averaging across other features of the object included in the design. Such inferences can be thought of as statements of the form: ``shifting an immigrant's country of origin from India to Poland increases favorability by X percentage points.'' In descriptive inference, conjoints provide information about both (a) the \textit{absolute} favorability of respondents toward objects with particular features or combinations of features, and (b) the \textit{relative} favorability of respondents toward an object with alternative combinations of features. Such inferences can be thought of as statements of the form ``Polish immigrants are preferred by X\% of respondents'' or ``Polish immigrants are more supported than Mexican immigrants, by X percentage points.'' Thus both causal and descriptive interpretations of conjoints are based upon the distribution of preferences across profile features and differences in preferences across alternative feature combinations.

Analytically, a fully randomized conjoint design without constraints between profile features is simply a full-factorial experiment (with some cells possibly, albeit randomly, left unobserved). All quantities of interest relevant to the analysis of conjoint designs therefore derive from combinations of cell means, marginal means, and the grand mean, as in the traditional analysis of factorial experiments. In a forced choice conjoint design, the \textit{grand mean} is by definition 0.5 (i.e., 50\% of all profiles shown are chosen and 50\% are not chosen). \textit{Cell means} are the mean outcome for each particular combination of feature levels. In the full-factorial design discussed by \citet{HainmuellerHopkinsYamamoto2014} and now widely used in political science, many or perhaps most cell means are unobserved. For example, in their candidate choice experiment, there are $2*6*6*6*2*6*6*6 = 186,624$ cell means but only 3,466 observations so about 98\% of cell means are unobserved. While this would be problematic for attempting to infer pairwise comparisons between cells, conjoint analysts mostly focus on the marginal effects of each feature rather than more complex interactions. Appendix \ref{app:quantities} provides detailed notation and elaborations of these definitions of quantities of interest.

In fully randomized designs, the average marginal component effects (AMCEs) are simply marginal effects of changing one feature level to another, all else constant. AMCEs therefore depend only upon \textit{marginal means}: that is the column and row mean outcomes for each feature level averaging across all other features. A marginal mean describes the level of favorability toward profiles that have a particular feature level, ignoring all other features. For example, in the common forced-choice design with two alternatives, marginal means have a direct interpretation as probabilities: a marginal mean of 0 indicates respondents select profiles with that feature level with probability $P(Y=1|X=x) = 0$ while a marginal mean of 1 indicates respondents select profiles with that feature level with probability $P(Y=1|X=x)=1$, where $Y$ is a binary outcome and $X$ is a vector of profile features.\footnote{It is not possible for the marginal mean to equal zero or one if pairs of profiles shown together are allowed to have the same level of a given feature (for example, both immigrants are from Germany). Instead, the marginal mean can range from the probability of co-occurrence to 1 minus that probability. If there are five levels of a feature, each shown with equal probability, then the probability of co-occurrence is $\frac{1}{5}*\frac{1}{5} = 0.04$ such that the marginal mean can take values in the range $(0.04,0.96)$. If the design is constrained so that features cannot be the same for both immigrants, then the marginal means fully range from zero to one. This constraint on the range of the marginal means also constrains the range of AMCEs. Notably, many conjoints provide features with only two levels, such as the male-versus-female candidate feature examined by \citet{TeeleKallaRosenbluth2018} or \citet{HainmuellerHopkinsYamamoto2014} in their conjoints on candidate choice. In such cases, the probability of co-occurrence is $\frac{1}{2}*\frac{1}{2} = 0.25$ bounding the AMCE for female (as opposed to male) candidates to the range $(-0.5, 0.5)$ if both candidates can have the same sex. Caution is therefore needed in comparing the relative size of features with few levels to features with many levels given that effects have different bounds.} With rating scale outcomes, marginal means can vary arbitrarily along the outcome scale used.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
\includegraphics[width=\maxwidth]{figure/hainmueller_candidate_replication-1} \caption[Replication of Hainmueller et al]{Replication of Hainmueller et al. (2014) Candidate Experiment using AMCEs and MMs}\label{fig:hainmueller_candidate_replication}
\end{figure}

@@

Because levels of features are randomly assigned, pairwise differences between two marginal means for a given feature (e.g., between candidates who are male versus female) have a direct causal interpretation. For fully randomized designs, the AMCE proposed by \citet{HainmuellerHopkinsYamamoto2014} is equivalent to the average marginal effect of each feature level for a model where each feature is converted into a matrix of indicator variables with one level left out as a reference category. This is no different from any other regression context wherein one level of any categorical variable must be omitted from the design matrix in order to avoid perfect multicollinearity.\footnote{In designs that entail constraints between profile features, the average marginal effect is a weighted average of effects across each combination of the constrained features where the weights on the effects are arbitrary but typically uniform. We ignore this distinction in the remainder of this article, as all of our results apply equally to fully randomized and to constrained designs.} This close relationship between AMCEs and marginal means is visible in Figure \ref{fig:hainmueller_candidate_replication} which presents a replication of the AMCE-based analysis of the Hainmueller et al. candidate experiment (left panel) and an analogous examination of the results using marginal means (right panel). Note, in particular, how marginal means convey information about the preferences of respondents for all feature levels while AMCEs definitionally restrict the AMCE for the reference category to zero (or undefined). For example, the AMCE for a candidate serving in the military is 0.09 (or a 9-percentage point) increase in favorability, reflecting marginal means for serving and non-serving candidates of 0.46 and 0.54, respectively. Similarly, the zero effect size for candidate gender reflects identical marginal means for male and female candidates (0.50 in each case). AMCEs in fully randomized designs are simply differences between marginal means at each feature level and the marginal mean in the reference category, ignoring other features.

The AMCE is often described as an estimate of the relative favorability of profiles with counterfactual levels of a feature. For example, \citet{TeeleKallaRosenbluth2018} summarize their conjoint on public support ``female candidates are favored [over men] by 7.3 percentage points'' (6). Similarly, \citet{HainmuellerHopkinsYamamoto2014} describe some of the results of conjoint on preferences toward political candidates:

@@

\noindent These examples make clear that despite the \textit{causal} inference potentially provided by the AMCE, the quantity of interest is frequently used to provide a characterization of a preferences that has a distinctly descriptive flavor about the relative \textit{levels} of support across profiles and also across subgroups of respondents. Indeed, this style of description is widespread in conjoint analyses. This use of conjoints to provide descriptive inferences about patterns of preferences is important because AMCEs are defined as \textit{relative} quantities, requiring that patterns of preferences are expressed against a baseline, reference category for each conjoint feature. A positive (negative) AMCE is read as higher (lower) favorability but it is only higher (lower) relative to whatever category serves as the baseline. For example, in the \citeauthor{HainmuellerHopkinsYamamoto2014} candidate example, choosing a non-religious candidate as a baseline means the AMCEs in the candidate experiment are all expressed relative to this non-religious baseline; the difference (if any) between other pairs of marginal means (e.g., evaluations of Mormon and Evangelical candidates) is not obvious. Relatedly, the negative direction (and the size) of the AMCEs for Mormon and Evangelical candidates would be different if the least-liked category (Mormon candidates) were the reference group. In that case, the AMCE for Evangelicals would be small and positive and the AMCEs for all other categories (including the presented reference category, ``none'') would be large and positive. More trivially, \citet{TeeleKallaRosenbluth2018} describe their comparisons about public preferences for female candidates relative to male candidates, but could have equivalent described patterns of equal size but opposite sign comparing preferences over male relative to female candidates.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
\includegraphics[width=\maxwidth]{figure/reference_category-1} \caption[Estimated AMCEs for Levels of the `Education' Feature for Each Possible Reference Category from Hainmueller et al.'s (2014) Immigration Experiment]{Estimated AMCEs for Levels of the `Education' Feature for Each Possible Reference Category from Hainmueller et al.'s (2014) Immigration Experiment}\label{fig:reference_category}
\end{figure}

@@

Though seemingly arbitrary, the choice of reference category for estimating AMCEs can be quite consequential.\footnote{Since this manuscript has been under review, we have been made aware of one working paper by \citet{ClaytonFerwerdaHoriuchi2018}, on the topic of immigration preferences, that correctly notes the need to address the arbitrary reference category in order to compare subgroup preferences.} For example, in \citeauthor{HainmuellerHopkinsYamamoto2014}'s candidate experiment (again, see \ref{fig:hainmueller_candidate_replication}), the least liked education level (``no formal education'') is chosen as a reference category, but the authors could have presented the results using any of the categories as the baseline. Figure \ref{fig:reference_category} shows how the estimated AMCEs for each level of the education feature would have differed depending on that choice. Selecting a reference category that receives middling support (i.e., more favorability than some other feature levels but less favorability than others), makes some AMCEs positive and others negative but all AMCEs can be made positive (or negative) simply by choosing a different baseline. The results would be numerically equivalent --- the alternative linear models used to the estimate the AMCEs have a mathematical equivalence --- but the choice has sizeable consequences for the interpretation of conjoint analyses, as we discuss below.\footnote{In \textit{constrained} conjoint designs, the choice of reference category is even more important. Consider, for example, the design of \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment, which constrains the ``Country of Origin`` feature so that levels `India,' `Germany,' `France,' `Mexico,' `Philippines,' and `Poland' cannot co-occur with the `Escape Persecution' level of the ``Reason for Application'' feature. Consequently, the AMCE for the ``Escape Persecution'' level (relative to the  ``Reunite with family'' reference category) is only defined for the subset of the design involving countries `China,' `Sudan,' `Somalia,' and `Iraq.' The AMCEs for those four countries (relative to India as a baseline) marginalize across all reasons for application, but the AMCEs for the first six countries marginalize only across the latter two reasons. Thus the interpretation of AMCEs --- and the basic ability to estimate them in constrained designs --- depends entirely upon the selection of a reference category where all feature levels can co-occur. In a design where \textit{all} features are constrained, then AMCEs are undefined for the design as a whole and only estimable for subsets of the design that are \textit{conditionally} unconstrained.}

@@

Given the need to choose a reference category for every feature in order to estimate AMCEs, an important question is: how do researchers decide which of tens of thousands of possible experimental cells should be selected as the reference category? Examining recently published conjoint analyses, it appears that the choice of reference category is either arbitrary or based upon substantive intuition about the meaning of feature levels. For example, \citet{HainmuellerHopkinsYamamoto2014} choose female immigrants as a baseline in their immigration experiment, thus providing an estimate of the AMCE of being male, while \citet{TeeleKallaRosenbluth2018} choose male candidates as a baseline in their conjoint, thus providing an estimate of the AMCE of being female. The choice is seemingly innocuous. Sometimes choices of reference category appear to be driven by substantive knowledge: on language skills of immigrants in their immigration experiment, \citet{HainmuellerHopkinsYamamoto2014} choose fluency as a baseline; on the prior trips to the US feature, ``never'' is chosen as the baseline.

% Difference in conditional AMCEs
\begin{table}
\caption{Uses of Subgroup Analysis Published in Political Science Journals}\label{tab:papers}
\begin{center}
\scriptsize
\begin{tabular}{p{1.5in} p{1.5in} p{1.5in} p{1.5in}}\toprule
\textbf{Paper} & \textbf{Journal} & \textbf{Topic} & \textbf{Subgroup Comparisons} \\ \midrule
\citet{BechtelScheve2013} & PNAS & Climate agreement preferences & Environmentalism and International Reciprocity Attitudes \\ \midrule
\citet{FranchinoZucchini2014} & PSRM & Candidate preferences & Political Interest, Left-right self-placement\\ \midrule
\citet{HainmuellerHopkinsYamamoto2014} & Political Analysis & Immigration preferences & Ethnocentrism \\ \midrule
\citet{HansenOlsenBech2014} & Politcal Behavior & Policy preferences & Partisanship \\ \midrule
\citet{Carlson2015} & World Politics & Candidate preferences & Co-ethnicity \\ \midrule
\citet{BansakHainmuellerHangartner2016} & Science & Immigration preferences & Left-right self-placement, age, education, income\\ \midrule
\citet{BallardRosaMartinScheve2016} & JOP & Tax preferences & Various\\ \midrule
\citet{Campbelletal2016} & BJPS & Candidate preferences & Partisanship \\ \midrule
\citet{CarnesLupu2016} & APSR & Candidate preferences & Partisanship \\ \midrule
\citet{Mummolo2016} & JOP & News selection & Various\\ \midrule
\citet{VivyanWagner2016} & EJPR & Candidate preferences & Political attitudes \\ \midrule
\citet{MummoloNall2017} & JOP & Mobility preferences & Partisanship \\ \midrule
\citet{BechtelGenoveseScheve2017} & BJPS & Climate agreement preferences & Employment sector emissions \\ \midrule
\citet{BechtelHainmuellerMargalit2017} & EJPR & International bailout preferences & Various\\ \midrule
\citet{GallegoMarx2017} & J. European Public Policy & Labor market policy & Left-right self-placement \\ \midrule
\citet{KirklandCoppock2017} & Political Behavior & Candidate preferences & Partisanship \\ \midrule
\citet{Sen2017} & PRQ & Judicial candidate preferences & Partisanship \\ \midrule
\citet{Sobolewskaetal2017} & J. Ethnic \& Migration Studies & Immigrant integration & Various \\ \midrule
\citet{EggersVivyanWagner2018} & JOP & Candidate preferences & Sex \\ \midrule
\citet{Hankinson2018} & APSR & Housing policy preferences & Various \\ \midrule
\citet{OliverosSchuster2018} & CPS & Bureaucrat candidate preferences & Various \\ \midrule
\citet{TeeleKallaRosenbluth2018} & APSR & Candidate preferences & Sex, Partisanship \\ \midrule
\citet{Careyetal2018} & Politics, Groups, and Identities & Hiring preferences & Various \\ \midrule
\bottomrule
\end{tabular}
\end{center}

All articles in this table use subgroup conditional AMCEs to make inferences about differences in preferences between subgroups.
\end{table}

While seemingly arbitrary and innocuous, the choice of reference category can provide highly distorted descriptive interpretations of preferences among subgroups of respondents. This occurs when researchers examine \textit{conditional} AMCEs, wherein AMCEs are calculated separately for subgroups of respondents and those conditional estimates are directly compared \citep[13]{HainmuellerHopkinsYamamoto2014}. Conditional AMCEs convey the causal effect of an experimental factor on overall favorability among the subgroup of interest. Consider, for example, a two-condition candidate choice experiment where Democratic and Republican respondents are exposed to either a male or female candidate and opinions toward the candidate serve as the outcome. It is sensible to imagine that effects of candidate sex might differ for the two groups and therefore to compare the size of treatment between the two groups. Perhaps Democrats are more responsive to candidate sex than are Republicans, making the causal effect larger for Democrats than Republicans. When conjoint analysts engage in subgroup comparisons, they are engaging in this kind of search for heterogeneous treatment effects across subgroups, but across a much larger number of experimental factors.

Discussions of conditional AMCEs in conjoint analyses often explicitly or implicitly engage in this kind of discussion comparing the size and direction of subgroup causal effects. Indeed, Table \ref{tab:papers} reports a list of recently published articles in political science that engage in this form of subgroup analysis. Given the common practice of descriptively interpreting conjoint experimental results, such subgroup analyses seem perfectly intuitive and the set of subgroups listed in the last column of Table \ref{tab:papers} contains some unsurprising covariates, such as partisanship, that are of obvious theoretical interest in almost any study of individual preferences. If interpreted as a difference in the size of the \textit{causal effect} for two groups, such comparisons are perfectly consistent with more traditional experimental analysis and a perfectly acceptable interpretation of the conjoint results.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
\includegraphics[width=\maxwidth]{figure/tkr_replication-1} \caption[Replication of Results for `Candidate Sex' Feature from Teele et al]{Replication of Results for `Candidate Sex' Feature from Teele et al. (2018) Candidate Experiment using Full Sample and Subgroup AMCEs and MMs}\label{fig:tkr_replication}
\end{figure}

@@

@@

\item Exercise caution when explicitly or implicitly interpreting differences-in-AMCEs across subgroups. Differences-in-AMCEs are differences in effect sizes for subgroups, not statments about the relative favorability of the subgroups toward profiles with a feature. Heterogeneous effects do not necessarily mean different underlying preferences. If differences in AMCEs are reported, the choice of reference categories should be discussed explicitly and diagnostics should be provided to justify it.

@@

\section{Bechtel and Scheve (2013) Climate Agreement Experiment}

\begin{knitrout}
